### 2023-01-25 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@026f64e8b2ee9a7eeddbf48f484c413be77d2a4e 🚀

%
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{1,2,‡}\quad %
\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
%
\,\textsuperscript{1,‡}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{1,2,3}\quad %
\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
%
\,\textsuperscript{4}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{2,5}\quad %
\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
%
\,\textsuperscript{7}\quad %
\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
%
\,\textsuperscript{2,3}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
%
\,\textsuperscript{2,5}\quad %
\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
%
\,\textsuperscript{8}\quad %
\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
%
\,\textsuperscript{9}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}

@@

\begin{figure}
\hypertarget{fig:embedding}{%
\centering
\includegraphics{figures/conceptual_2.png}
\caption{The embedding process (\textbf{A}) can help to identify links
(interactions) that may have been missed within the current sample
(community, \textbf{B}), while transfer learning (\textbf{D}) allows for
predicting links (interactions) for species external to the original
sample as well as within sample links (\textbf{F}). Transfer learning
allows for the prediction links (interactions) when novel species
(\textbf{C}) are included in the sample by learning using other relevant
predictors (e.g.~traits) in conjunction with the known interactions to
infer latent values (\textbf{E}). Within this context the predicted
networks as well as the ecological predictors used (green boxes) are
products that can be quantified through field measurements, whereas the
embedded as well as imputed matrices are representative of
\textbf{TK}}\label{fig:embedding}
}
\end{figure}

>>>>

%
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{1,2,‡}\quad %
\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
%
\,\textsuperscript{1}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{1,2,3}\quad %
\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
%
\,\textsuperscript{4}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{2,5}\quad %
\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
%
\,\textsuperscript{7}\quad %
\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
%
\,\textsuperscript{2,3}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
%
\,\textsuperscript{2,5}\quad %
\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
%
\,\textsuperscript{8}\quad %
\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
%
\,\textsuperscript{9}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}

@@

\begin{figure}
\hypertarget{fig:embedding}{%
\centering
\includegraphics{figures/conceptual_2.png}
\caption{The embedding process (\textbf{A}) can help to identify links
(interactions) that may have been missed within the original community
(represented by the orange dashed lines, \textbf{B}). Transfer learning
allows for the prediction links (interactions) when novel species
(\textbf{C}) are included alongside the original community (\textbf{D}).
This is achieved by learning using other relevant predictors
(\emph{e.g.} traits) in conjunction with the known interactions to infer
latent values (\textbf{E}). Ultimately this allows us to predict links
(interactions) for species external to the original sample as well as
within sample links (\textbf{F}). Within this context the predicted (and
original) networks as well as the ecological predictors used (green
boxes) are products that can be quantified through field measurements,
whereas the embedded as well as imputed matrices are representative of a
decomposition of the interaction networks}\label{fig:embedding}
}
\end{figure}
